Verifying Demonstrations

### 2019-02-20 paper/verifiability-analysis.tex
Fixes remaining adversary stuff in verifiability-analysis

\subsubsection{Designated protest}%
\label{analysis-designated}

@@

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
available from a public and permanent storage.
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger and storage (\(\TS\), \cref{timestamp}).
For both \cref{in-system-adversary,deanonymizing-storage-adversary} we assumed 
an honest-but-curious adversary controlling \(\TS\)\footnote{%
  We note that, in general, distributed (decentralized) ledgers cannot 
  withstand a malicious \ac{ISP}.
  Such an adversary can partition the network and provide Alice and Bob with 
  different views of the ledger, thus breaking individual verifiability.
  However, this requires that the adversary \emph{can observe} Alice's and 
  Bob's channels to the ledger --- which is still not true even for 
  \cref{deanonymizing-storage-adversary}.
}.
This means that Alice can check that her proof share is indeed there.

>>>>

\subsubsection{Designated use}%
\label{analysis-designated}

@@

\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
that their participation proofs (\ie proof shares) are indeed included in the 
computed count.
All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
available from a public and permanent storage.
Thus, Alice and Bob can simply check that all of their proof shares are indeed 
there and the security of individual verifiability depends on the properties of 
the ledger and storage (\(\TS\), \cref{timestamp}).

We assumed an honest-but-curious adversary controlling \(\TS\)\footnote{%
  We note that, in general, distributed (decentralized) ledgers cannot 
  withstand a malicious \ac{ISP}.
  Such an adversary can partition the network and provide Alice and Bob with 
  different views of the ledger, thus breaking individual verifiability.
  However, this requires that the adversary \emph{can observe} Alice's and 
  Bob's channels to the ledger.
}.
This means that Alice can check that her proof share is indeed there.
